---
title: "ADA Data table"
author: "Michael C"
date: "2024-04-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Setup ----------------------------------------------------------------

## 1a. Load libraries -----

```{r basics}
library(tidyverse);library(lubridate) 
# Utility 
library(here);library(janitor);library(clipr) 

# Excel loops, nested data 
library(readxl);library(openxlsx);library(purrr) 

# Table 
library(DT);library(htmlwidgets)

#CMAP Specific
library(cmapplot)
library(cmapgeo)
```

## 1b. Options -----

```{r Options, call stored Census API key, load fonts}

# options(scipen = 1000, stringsAsFactors = FALSE)



```

# 2. Ingest data ----------------------------------------------------------

## Excel workbook download (manual)

## Read in data

```{r readindata}
ada_raw <- read_excel("240314_ADACompliance.xlsx") %>% clean_names()



```

# 3. Clean data -----------------------------------------------------------

# Select columns for table, all towns

```{r selectcolumns}
ada_clean_all <- ada_raw %>%
  select(what_is_the_entity_name, is_a_transition_plan_required, does_the_community_have_a_self_evaluation_plan, does_the_community_have_a_transition_plan, was_an_ada_coordinator_designated, is_there_a_publicly_available_grievance_procedure_for_the_ada, is_there_a_publicly_posted_notice_about_rights_under_the_ada, when_was_the_self_evaluation_plan_created_or_most_recently_updated, link_to_the_self_evaluation) %>% arrange(what_is_the_entity_name) 

```

# Clean ada_clean_all

```{r cleanada}

ada_clean_all <- ada_clean_all %>% 
# Binaries to Yes/No if only 1 and 0, add N/As if exist
  mutate(across(c(is_a_transition_plan_required, does_the_community_have_a_self_evaluation_plan, does_the_community_have_a_transition_plan, was_an_ada_coordinator_designated, is_there_a_publicly_available_grievance_procedure_for_the_ada, is_there_a_publicly_posted_notice_about_rights_under_the_ada,), .fns = ~case_when( as.character(.) == "1" ~ "Yes", as.character(.) == "0" ~ "No", 
                                                                                                                                                                                                                                                   # Handle N/As 
  is.na(.) ~ "N/A", TRUE ~ "N/A"))) %>% 
  # Format date field
  mutate("when_was_the_self_evaluation_plan_created_or_most_recently_updated" = excel_numeric_to_date(as.numeric(when_was_the_self_evaluation_plan_created_or_most_recently_updated))) 
```

# Create hyperlink for table ada_clean_all

```{r adacleanallhyper}
ada_clean_all <- ada_clean_all %>% mutate("pdf_link" = paste0('<a href="',
                             link_to_the_self_evaluation,
                             '" target="_blank">', what_is_the_entity_name, '</a>')) %>% relocate(pdf_link, .before = 1)



```

# 4. DataTable ------------------------------------------------------------

## Background

R DT package, wrapper for the JavaScript DataTables library

Vignettes: <https://rstudio.github.io/DT/>

Documentation: <https://cran.r-project.org/web/packages/DT/DT.pdf>

## Handle N/As for Date

```{r nasfordate}
rowCallback <- c( "function(row, data){", " for(var i=0; i<data.length; i++){"," if(data[i] === null){"," $('td:eq('+i+')', row).html('N/A')"," .css({'color': 'rgb(151,151,151)', 'font-style': 'italic'});"," }"," }","}")



```

## Create table

```{r adadt}

ada_dt <- datatable(ada_clean_all %>% 
# Tidy df for table
  rename("entity_name" = pdf_link) %>% arrange(what_is_the_entity_name) %>% select(-what_is_the_entity_name, -link_to_the_self_evaluation), 

  #Column search bars
filter = 'top',

#Column name reformatting
colnames = c('Municipality' = 1, 'Is a transition plan required' = 2, 'Self-evaluation' = 3, 'Transition Plan' = 4, 'ADA Coordinator?' = 5, 'Publicly available ADA grievance procedure' = 6, 'Publicly posted notice of ADA rights' = 7, 'when was the plan last updated?' = 8),


  
# Formatting options, escape = FALSE to allow hyperlink HTML formatting 
extensions = "Scroller", escape = FALSE, style = "auto", class = "cell-border stripe", rownames = FALSE, width = "100%", options = list(# Page options dom = ("Bfrti"), pageLength = -1, searchHighlight = TRUE, 
 

   # Scroll options 
  # Set Y scroll as function of iframe height in ArcGIS Hub (550px)
  scrollY = 550 - 200, scrollX = TRUE, scroller = TRUE, 
  # Column headers 
  fixedHeader = FALSE, # N/A date fill rowCallback = JS(rowCallback), 
  
  
  # Add font family
  initComplete = JS( "function(settings, json) {", "$('body').css({'font-family': 'Whitney'});", "}") )) 
#%>% 
  # Column formatting
 # DT::formatDate(ada_dt, "Plan most recently updated"  method = #"toLocaleDateString") 


```

# View datatable

```{r viewada_dt}
ada_dt

```

### Export as widget (local/sharing option)

```{r exportaswidget}

htmlwidgets::saveWidget(widget = ada_dt, file = "ada_transition_plans_dt.html", selfcontained = TRUE)



```

### Export as widget for GitHub Pages (requires index.html name)

```{r githubexport}

htmlwidgets::saveWidget(widget = ada_dt, file = "index.html", selfcontained = TRUE)
```
